\chapter*{Acknowledgments}\label{ch:acknowledgments}
My time in Tennessee has been some of the most enriching, fun, and frustrating time in my life.  Through my time here I have had one stead fast pillar that supported me through it all, Megan.  I could never thank you nor love you enough.

\par
To my family. I would like to thank my father, Jaime.  For shaping me into the man I have become and for the long hikes and backpacking trips that we've done together.  He helped curate my love and passion for being in the outdoors.  I would like to give a very special thanks to my sister Ali, her husband Adam, to my amazing nieces Amara, Amelia, and my equally amazing nephew Alyas.  I would also like to thank Nancy, Jim, and Lindsey along with all the members of the Carr and Stobie families for making me feel like a part of them.  

\par
Thank you to my friend Saul.  For all the great memories we've had growing up together, for the crazy trips to India and Mexico, and for taking a Grey Hound from San Francisco to Knoxville to visit me.  

\par
I would like to deeply thank the heavy ion group at the University of Tennessee for the support they gave me and the guidance.  I would like to Soren Sorensen and Christine Nattrass for their guidance.  To Rebecca and Kyle for becoming life long friends.  To Pat, Redmer, and Adam for giving me input and trouble shooting on the analysis.

\par 
I would also like to thank the members of my committee; Christine Nattrass, Ken Read, Soren Sorensen, and Ivan Maldonado. 

